R Notebook

### 2021-03-13 eda.Rmd
Added some results from discussion

@@

```{r}
ggplot(streetrx, aes(x=ppm)) + geom_histogram(bins = 50)
```

@@

```{r}
streetrx$price_date <- as.Date(streetrx$price_date, format= '%m/%d/%y')
streetrx <- streetrx %>% mutate(year = lubridate::year(price_date),
                                month = lubridate::month(price_date),
                                day = lubridate::day(price_date))
```

@@

@@

>>>>

Keep, log transform

@@

```{r}
ggplot(streetrx, aes(x=log(ppm))) + geom_histogram(bins = 50)
```

@@

```{r}
streetrx$price_date <- as.Date(streetrx$price_date, format= '%m/%d/%y')
streetrx <- streetrx %>% mutate(year = lubridate::year(price_date),
                                month = as.factor(lubridate::month(price_date)),
                                day = lubridate::day(price_date))
```

I wouldn't think we should include year, as presumably we're going to be using this for future data, for which we'll have a new year. What about month? We'll use median because there are some extreme ppm values

```{r}
streetrx %>% group_by(month) %>% summarise(med_ppm = median(ppm))
```

An F test shows that we cannot reject the possibility that this variance is simply due to chance:

```{r}
aov(ppm ~ month, data = streetrx) %>% summary()
```

@@

Recode missing as "missing"

@@

Missing (empty), internet (interet pharmacy, url, google), heard it, personal, other
